\Large \bf \sys: Library-Oriented Program Analysis

### 2020-05-27 paper/draft.tex
Massive rewrite

\newcommand{\fra}{fragmentation\xspace} % fracture?
\newcommand{\ana}{analysis\xspace}      % 
\newcommand{\ass}{reassembly\xspace}    % 
\newcommand{\Fra}{Fragmentation\xspace} % fracture?
\newcommand{\Ana}{Analysis\xspace}      % 
\newcommand{\Ass}{Reassembly\xspace}    % 
\newcommand{\dia}{\fra, \ana, and \ass}

@@

Effort and performance costs are severely compounded by the use of third-party libraries, usually glued together without a full understanding of their internals.
This is a recent phenomenon enabled by zero-cost code sharing~\cite{libs}:
  language-specific package repositories eliminate the cost of publishing and using a library.
As a result, applications frequently count hundreds of libraries~\cite{npmstudy:19}, with each one often only a few lines long~\cite{leftpad, npmstudy:19}. % how to say thousands of them depend on a 11-line lib?
Library-oriented analysis adds to the challenges of prior tools as
  (i) library boundaries disappear at runtime, and
  (ii) coarse-grained, high-level language semantics misalign with fine-grained, low-level instrumentation.

To address these challenges, we propose a novel approach to dynamic analysis, targeting dynamic programming languages---and implemented in \sys for the server-side JavaScript ecosystem (>1.3M libraries~\cite{modulecounts}). 
\sys leverages the ability of these languages to import code at runtime as a string in order to apply transformations that wrap the module about to be imported with developer-provided, analysis-specific code.
More specifically, \sys inserts a series of steps in the module-loading process result in wrapping a library's full observable behavior---rather than just its interface---and exposing it to developers for runtime analysis.
\sys effectively fragments, transforms, and reassembles the application at the level of individual libraries. 
The overall approach has several practical benefits over prior work:
  (i) it allows bolting the dynamic analysis as a library  onto unmodified runtime environments,
  (ii) it supports analyses expressed using the same language, tools, and abstractions as the program language,
  (iii) it features low runtime performance overheads, enabling the potential for toggling its use in production environments.

@@

To demonstrate that \sys can be useful in practice, despite its coarse granularity, we develop a diverse set of analyses:
  a read-write-execute security analysis,
  a profiling analysis for identifying bottlenecked modules,
  and an analysis extracting union-based type invariants.
% These analyses drive \sys's design requirements, and highlight the decisions behind its design.
Each of these analyses takes about 100 LoC in JavaScript;
  this integration between the code being analyzed and the one implementing the analysis has significant usability implications.
Finally, \sys's performance is evaluated extensively, using
  (i) over 50 popular libraries and scripts, highlighting compatibility and performance improvements over state-of-the-art frameworks;
  (ii) three full applications, demonstrating that \sys scales to large and complex programs; and
  (iii) a series of micro-benchmarks that zoom into a few specific characteristics of \sys.
\S\ref{bg}--\ref{eval} present our key contributions:
\begin{itemize}
\item \S\ref{bg} characterizes the shared needs of three case-study multi-module analyses whose needs remain mostly by general-purpose analysis frameworks.
\item \S\ref{design} presents the design of \sys, bolt-on library-oriented dynamic analysis~\sx{design}, which meets the requirements of the three case-study analyses.
\item \S\ref{impl} discusses our implementation, \sys, as a pluggable library for the JavaScript ecosystem, as well as the implementation of the three analyses.
\item \S\ref{eval} evaluates \sys, showing that it expresses insightful analyses succinctly, adds minimal overheads over the baseline runtime, and scales to hundred-library programs.
\end{itemize}

The paper then discusses \sys's limitations and its application to other languages~\sx{diss};
  it compares with related prior work~\sx{rw};
  and draws appropriate conclusions~\sx{end}.

@@

A library, package, or module---we use these terms interchangeably---is a development-time construct encapsulating reusable functionality.
This functionality falls into two categories:
  it either (i) comes bundled with the language, possibly wrapping operating-system interfaces, such as the file-system, in a way that is system-agnostic and conforms to the language's conventions,
  or (ii) is provided by other developers sharing code others might find useful.
Fig.~\ref{fig:ex1} shows a \ttt{simple-math} library (right) imported by a program (left).

@@

From the programming language's perspective, the process of \ttt{import}ing a library is achieved in several steps. 
Compiled languages support separate compilation, where source files are compiled individually, followed by a runtime-linking phase that loads and links the resulting object files.
Interpreted languages involve a somewhat convoluted process that combines runtime loading, interpretation, and linking.
This process starts by locating the library in the file system,
% or across the network,\footnote{
%   Examples of run-time environments featuring network loading include V8 and deno, for executing JavaScript and TypeScript respectively.
% }
by resolving code-relative module identifiers.
The content of the library is then read and wrapped in a way that resolves library-local names, such as \ttt{\_\_name\_\_} in Python and \ttt{\_\_filename} in JavaScript, to meaningful values.
The wrapper is then interpreted and evaluated using the language's interpreter, which might result to side-effects---for example, a \ttt{process.exit()} in the library's top-level scope will exit the entire program.
Finally, the value bound to the \ttt{export}ed interface or returned from this interpretation (depending on the language) is made available to the scope of the  \ttt{import}ing code.

There is significant variation, but a few features are common across many implementations.
A library cache maintains a mapping from library identifiers, often absolute paths, to returned \ttt{export} values.
The cache serves a dual purpose:
  by avoiding locating already loaded libraries, it improves performance and ensures the consistency of any library-internal state.
Recursive imports are handled in a depth-first way, and when cyclical dependencies are possible, they are resolved by pointing to the cache.
An increasingly common feature is to allow different versions of the same library to co-exist in a program, in order to avoid a choice between mutually exclusive options---a paradoxical situation known as ``dependency hell''.
As a result, a single \ttt{import} $l$ does not necessarily resolve to the same (version of the) library $l$ every time.
The dual of this is also possible: two different library names may resolve to the same identifier (in which case the second will be redirected to the cache).
These features complicate library-level analysis, especially in interpreted programming languages.

@@

As a concrete example, consider the recent \ttt{event-stream} incident~\cite{es1, es2}, in which a maintainer of a highly popular library inserted code stealing Bitcoin wallet credentials from programs using that library.
Heavy-weight, offline dynamic analysis~\cite{jalangi} would not have helped, as \ttt{event-stream} activated only on production (rather than testing or development).
Coarse-grained analysis at program boundaries, say via containment or system-call interposition~\cite{systrace:03}, would have not helped either because host programs already used the network and disk.
Finally, static analysis would have been of little use, as \ttt{event-stream} encrypted its malicious payload.

Having the ability to toggle a library-level ``allow-deny'' security analysis on/off at runtime would have revealed the (unusual) resources touched by \ttt{event-stream}.
Analyzing the behavior \emph{within} the library itself is not critical:
  if any data exfiltration is happening, it will require calling out of the library and into the network---in \ttt{event-stream}'s case, using the \ttt{fs} library to modify a different library and then call \ttt{http} from the second library.
Both \ttt{fs} and \ttt{http} are part of the standard library, built into the runtime environment.
Examples of interfaces outside the \ttt{http} and \ttt{fs} libraries include the ability to use global variables, import other libraries, and access the cache of the loaded modules---all of which are unfortunately available to any third-party that is part of an application.
% The key issue underlying the \ttt{event-stream} attack is that any third-party fragment of an application has unrestricted access to the functionality available to the rest of application.

@@

Switching-on a library-level profiling analysis 
  would quickly detect a slowdown and attribute it to the bottlenecked \ttt{minimatch}.
Wrapping library interfaces with profiling logic would collectively construct a model of the current workload.
Such profiling could operate at a high resolution in time and space---at every function call entering a library and on hundreds of libraries across an application---but does not need to track detailed operations such as direct variable accesses.
Each library wrapper can collect profiling statistics at its own boundary, aggregating summaries into a global structure ordering libraries by resource consumption.

\heading{Type Invariant Discovery}
Extracting type information in a program is helpful in a variety of different ways. %, as type safety is an important property helpful in variety of scenarios. 
For example, types can be used to (i) identify program invariants to be preserved during code modifications, (ii) generate (machine-checkable) program documentation, or (iii) guide program synthesis and regeneration~\cite{daikon}.
This is especially important in dynamic programming languages:
  in the absence of static type signatures, there is not much one can say about an object without executing it and inspecting its properties.

As a case in point, consider the \ttt{gRPC} library for serializing and de-serializing objects~\cite{grpc}.
To use it, developers have to provide a protocol-buffer specification describing the types of values that will be serialized.
Given a library---say, bignum or crypto---a developer has to first call it manually, take note of the result's type, and then fill in the protobuf spec.
This process has to be repeated with every change, often due to library updates or changes in the consuming program's structure.

Library-level dynamic analysis can be used to discover such type assertions or invariants.
The analysis would consult the (static) definition of a type \emph{system}, capturing the type of values at the boundaries of libraries by observing their arguments during the execution of the program.
%% TODO: such as the simply-typed lambda calculus augmented with objects and union types.

@@

  \item \textbf{Fragmentation:}
\sys starts by recursively dismantling a program into its dependencies. % ---pieces of software implement a computation or functionality.
This is achieved by re-wiring the language's \ttt{import} function to go through \sys, resulting in \sys walking the program's recursive dependency structure at runtime.
During this phase, \sys has to determine the granularity of the analysis (\eg top-level libraries, a specific library \etc) in order to apply transformations at the correct level and map the provided analysis hooks to the corresponding libraries.

@@

  \item \textbf{Reassembly}
Finally, \sys reassembles individual modified libraries back into the program's original structure.
The most important challenge during this phase is the treatment of the library cache~\sx{bg1}.
The cache needs to be augmented to support multiple wrappers per library, each capturing a small fragment of the overall analysis.
% without breaking the program's semantics.
% ensure every fragment finds its place during dependency reassembly,

@@

\subsection{Fragmentation}
\label{one}

When a \sys-augmented program starts, it first loads the analysis file provided by the developer. 
The file may specify a subset of libraries whose boundaries are of interest or a subset of libraries that should \emph{not} be analyzed.
Among other things, \sys needs to determine the library boundaries of interest and the granularity of analysis.
To do this, it extracts a static approximation of the dependency graph by traversing library files.
Using this graph, it processes the analysis file to extract a mapping from library identifiers to analysis hooks.
It also checks for constructs not associated with libraries---for example, whether the analysis includes global variables, library-local constructs, standard libraries \etc
\sys then proceeds to dynamically replace the implementation of \ttt{import} and launch the program:
  rather than simply locating and loading a library, calls to \ttt{import} now yield to \sys.

@@

%FIXME: Needs examples, especially the context
For each analyzed library, \sys needs to place hooks all around its boundary---not just its interface (Fig.~\ref{fig:shadowing}).
This is achieved in three logical steps:
(i) transforming library's context, a mapping from names to values that are available from outside library,
(ii) interpreting the library within this context, so that all names bind and resolve to \sys-augmented values, and
(iii) transforming the library's \ttt{export} value, \ie the library interface, once the interpretation is complete.
Before discussing \emph{where} each transformation is applied, however, we show \emph{how} they are applied.

@@

To achieve this, \sys first needs to prepare a transformed copy of the library's outer context.
Semantically, the context is a map from variable names to their values.
Thus, \sys creates an auxiliary hash table mapping names to transformed values.
Names correspond to any name that, by the language definition, is accessible by the library and resolves to a value outside that library, such as globals, built-ins, module-locals, \etc
Transformed values are created by applying \ttt{wrap} to values in the context, adding the provided analysis hooks.

@@

This section details our implementation of \sys for server-side JavaScript in about 1.5K lines of code on top Node.js v8.9.4~\sx{impl1}, and 
% We start with the internals of \sys's implementation, and then describe
including the three analyses developed atop \sys~\sx{impl2}.
Discussion of how other environments diverge from JavaScript is left for the next section~\sx{reqs}.

@@

% The resolution algorithm is somewhat convoluted, because it depends on several different facts (including the type of the file requested, whether it is a globally installed, whether it is a directory \etc).
% It does not require any \sys support beyond copying the directory that contains the source code of the all the modules onto the remote host.
% \sys interposes on all of these steps to facilitate transformations.
\sys augments all of these steps.
Interposing on resolution (R) makes the module identifier available to \sys without affecting the (incredibly convoluted!) module resolution algorithm.
If the module's type corresponds to a module that can be analyzed by \sys, \sys fetches the corresponding analysis during loading (L).
Wrapping (W) and evaluation (E) are where \sys transforms the module boundary.
\sys replaces Node's wrapper function to pass an additional argument, the modified context \ttt{CTX}.
\sys comes with a hard-coded list of names corresponding to the specific versions of EcmaScript and Node.
Identifying names coming from EcmaScript was relatively easy, as the standard makes them explicit.
Node's global names are described at various parts of the documentation, but library-local names required close inspection of Node's internals; fortunately, they were only five names.

@@

As the three analyses are quite complex to include in the paper, we present here a trivial analysis---one that counts all accesses to global variables from a module \ttt{serial}:

@@

\heading{Security Analysis}
To address the security concerns of third-party libraries, we developed a concrete \ttt{RWX} policy that analyzes accesses for every library-to-library combination.
The analysis treats built-in libraries and global variables as modules,
% and generates a list of permissions for each of their fields.
and develops a permission model where individual fields are governed by permission sets containing combinations of read, write, and execute permissions:
 (i) a read permission (\R) indicates that a consumer read a value, including assigning it to a variable and passing it around to other modules;
 (ii) a write permission (\W) indicates that a consumer modified or deleted a value; and
 (iii)  an execute permission (\X) indicates that a consumer executed a value---\eg a function or a method---or invoked a constructor (usually prefixed by \ttt{new}).

The resulting permission sets are organized as collections of maps, one per library, indexed by object-paths---\eg \ttt{require("Math").add: RX}.
% that correspond to values of other modules or global-like language names.

@@

  \item \textbf{Q3} How does it perform? We answer this question here.
  For the most libraries, \sys overheads are under 5\%~\sx{meso}.
  \sys is about $22\times$ \todo{faster} than Jalangi, a state-of-the-art dynamic analysis framework~\sx{meso}.
  By executing on unmodified runtimes, \sys has significantly better compatibility:
    to execute, Jalangi requires significant library modifications~\sx{meso}.
  \sys scales to three large applications with hundreds of libraries while interposing on several thousands of objects~\sx{macro}.
  Most of the overheads come from tracking global variables, but loading-time wrapping and runtime interposition overheads are negligible~\sx{micro}
  % The majority of the overheads come from the use of \ttt{with}, a

@@

\begin{figure*}[t]
  \centering
   \includegraphics[width=\textwidth]{./figs/micro-packages.pdf}
  \caption{
    \textbf{Analysis performance overhead.}
    The plot shows the performance overhead of the three analyses for 45 libraries~\cf{meso}.
  }
  \label{fig:micro-packages}
  \vspace{-3mm}
\end{figure*}

@@

In terms of analysis, both systems are configured to perform dynamic frequency analysis of accesses to global variables.
The analysis is a common denominator between \sys and Jalangi, designed and implemented from scratch to ensure a fair and meaningful comparison between the two frameworks.
Such analyses are useful for understanding how programs with third-party libraries interact with global state---\eg for generating remote-procedure stubs or scaling out functional components~\cite{ignis}.

Fig.~\ref{fig:meso} presents the comparison between \sys and Jalangi.
The core of the analysis requires a few lines, but expressing it in \sys requires 4$\times$ fewer lines of code;
  the effort of employing \sys as a library was also significantly lower than that of Jalangi2, for which we relied on a Docker container to simplify the framework's setup.
The performance results show that \sys performs better than Jalangi2, at times by a significant margin (\ie more than 10$\times$ for 13 benchmarks).
Jalangi2 is more powerful than \sys, capable of expressing analyses that are more fine-grained than \sys's, but results in higher developer effort and runtime performance.

@@

\begin{table}[b]
\center
\footnotesize
\setlength\tabcolsep{3pt}
\caption{
  \footnotesize{
    \textbf{Applying \sys to three large applications}.
    The table shows the overheads of applying the three analyses to three large applications~\cf{macro}.
  }
}
\begin{tabular*}{\columnwidth}{l @{\extracolsep{\fill}} ccc}
\toprule
                                     & KoaBlog~\cite{koa}    & Moeda~\cite{moeda}   &  Term/zr~\cite{terminalizer} \\
\midrule
Structure                            &                   &                      &              \\
~~Size (MB)                          & 41                &  29                  &   262        \\
~~Code Size (KLoC)                   & 127               &  79                  &   39         \\
~~Top-level Modules, statically      &  24               &  7                   &    33         \\
~~Total Modules, statically (npm)    &  432              &  260                 &    1084       \\
~~Total Modules, dynamically (\sys)  &  1507             &   729                &     2355      \\
%                                     &                   &                      &              \\
Performance                          &                   &                      &              \\
~~Baseline                           &  0.97             &  1.27                &    0.754      \\
~~Security Analysis                  &  1.48             &  2.00                &    3.346      \\
~~Performance Diagnosis              &  1.30             &  2.684               &    2.684      \\
~~Type Invariant Discovery           &  1.32             &  2.036               &    2.615      \\     
\bottomrule
\end{tabular*}
\label{tab:macro}
\vspace{-5mm}
\end{table}

@@

The differences between the number of sub-modules detected statically (by \ttt{npm ls}) and the ones observed by \sys are due to a few reasons.
One is that \sys does not report accesses if a library has not been accessed at runtime, whereas \ttt{npm} traverses and reports on the entire dependency structure.
\sys analyzes modules that are part of the standard library (some of which have themselves internal dependencies),  not shown by \ttt{npm}.
Finally, \sys generates several different return wrapped objects for the same libraries~\sx{three}.

>>>>

\newcommand{\fra}{fracture\xspace} % fracture?
\newcommand{\ana}{analysis\xspace}      % 
\newcommand{\ass}{reassembly\xspace}    % 
\newcommand{\Fra}{Fracture\xspace} % fracture?
\newcommand{\Ana}{Analysis\xspace}      % 
\newcommand{\Ass}{Reassembly\xspace}    % 
\newcommand{\dia}{\fra, \ana, and \ass}

@@

Effort and performance costs are severely compounded by the use of third-party libraries,\footnote{
  The terms library, package, and module are used interchangeably.
}
often glued together without full understanding of their internals~\cite{libs}.
% This is a recent phenomenon enabled by zero-cost code sharing
%   language-specific package repositories eliminate the cost of publishing and using a library.
Applications frequently count hundreds of libraries~\cite{npmstudy:19}, each one often only a few lines long~\cite{leftpad, npmstudy:19}. % how to say thousands of them depend on a 11-line lib?
Library-oriented analysis adds to the challenges of prior tools as
  (i) library boundaries disappear at runtime, and
  (ii) coarse-grained, high-level language semantics misalign with fine-grained, low-level instrumentation.

This paper presents a novel approach to dynamic analysis, targeting dynamic programming languages---and implemented in \sys for the server-side JavaScript ecosystem (>1.3M libraries~\cite{modulecounts}). 
\sys leverages the ability of these languages to import code at runtime as a string in order to apply transformations that wrap the module about to be imported with developer-provided, analysis-specific code.
More specifically, \sys inserts a series of steps in the module-loading process result in wrapping a library's full observable behavior---rather than just its interface---and exposing it to developers for runtime analysis.
\sys effectively fragments, transforms, and reassembles the application at the level of individual libraries. 
The overall approach has several practical benefits over prior work:
  (i) it allows bolting the dynamic analysis as a library  onto unmodified runtime environments,
  (ii) it supports analyses expressed using the same language, tools, and abstractions as the program language,
  (iii) it features low runtime performance overheads, enabling toggling its use in production environments.

@@

To demonstrate that \sys can be useful in practice, despite its coarse granularity, we develop a diverse set of analyses:
  a read-write-execute security analysis,
  a profiling analysis for identifying bottlenecked modules,
  and an analysis extracting union-based type invariants.
% These analyses drive \sys's design requirements, and highlight the decisions behind its design.
Each of these analyses takes about 100 LoC in JavaScript;
  this integration between the code being analyzed and the one implementing the analysis has significant usability implications.
Finally, \sys's performance is evaluated extensively, using
  (i) over 50 popular libraries and scripts, highlighting compatibility and performance improvements over state-of-the-art frameworks;
  (ii) three full applications, demonstrating that \sys scales to large and complex programs; and
  (iii) a series of micro-benchmarks that zoom into a few specific characteristics of \sys.
\S\ref{bg}--\ref{eval} present our key contributions:
\begin{itemize}
\item \S\ref{bg} characterizes the shared needs of three case-study multi-module analyses whose needs remain mostly by general-purpose analysis frameworks.
\item \S\ref{design} presents the design of \sys, bolt-on library-oriented dynamic analysis~\sx{design}, which meets the requirements of the three case-study analyses.
\item \S\ref{impl} discusses our implementation, \sys, as a pluggable library for the JavaScript ecosystem, as well as the implementation of the three analyses.
\item \S\ref{eval} evaluates \sys, showing that it expresses insightful analyses succinctly, adds minimal overheads over the baseline runtime, and scales to hundred-library programs.
\end{itemize}
\noindent
The paper then discusses \sys's limitations and its application to other languages~\sx{diss};
  it compares with related prior work~\sx{rw};
  and draws appropriate conclusions~\sx{end}.

@@

Libraries are development-time construct encapsulating reusable functionality.
This functionality falls into two categories:
  it either (i) comes bundled with the language, possibly wrapping operating-system interfaces, such as the file-system, in a way that is system-agnostic and conforms to the language's conventions,
  or (ii) is provided by other developers sharing code others might find useful.
Fig.~\ref{fig:ex1} shows a \ttt{simple-math} library (right) imported by a program (left).

@@

From the programming language's perspective, the process of \ttt{import}ing a library is achieved in several steps. 
Compiled languages support separate compilation, where source files are compiled individually, followed by a runtime-linking phase that loads and links the resulting object files.
Interpreted languages involve a somewhat convoluted process that combines runtime loading, interpretation, and linking.
This process starts by locating the library in the file system,
% or across the network,\footnote{
%   Examples of run-time environments featuring network loading include V8 and deno, for executing JavaScript and TypeScript respectively.
% }
by resolving code-relative module identifiers.
The content of the library is then read and wrapped in a way that resolves library-local names, such as \ttt{\_\_name\_\_} in Python and \ttt{\_\_filename} in JavaScript, to meaningful values.
The wrapper is then interpreted and evaluated using the language's interpreter, which might result in side-effects---for example, a \ttt{process.exit()} in the library's top-level scope will exit the entire program.
Finally, the value bound to the \ttt{export}ed interface or returned from this interpretation (depending on the language) is made available to the scope of the  \ttt{import}ing code.

There is significant variation, but a few features are common across many implementations.
A library cache maintains a mapping from library identifiers, often absolute paths, to returned \ttt{export} values.
The cache serves a dual purpose:
  by avoiding locating already loaded libraries, it improves performance and ensures the consistency of any library-internal state.
Recursive imports are handled in a depth-first way, and when cyclical dependencies are possible, they are resolved by pointing to the cache.
An increasingly common feature is to allow different versions of the same library to co-exist in a program, in order to avoid a choice between mutually exclusive options---a paradoxical situation known as ``dependency hell''.
As a result, a single \ttt{import} $l$ does not necessarily resolve to the same (version of the) library $l$ every time.
The dual of this is also possible:
   two different library names may resolve to the same identifier (\ie point to the same cache entry).
These features complicate library-level analysis, especially in interpreted programming languages.

@@

As a concrete example, consider the recent \ttt{event-stream} incident~\cite{es1, es2}, in which a maintainer of a highly popular library inserted code stealing Bitcoin wallet credentials from programs using that library.
Heavy-weight runtime instrumentation~\cite{jalangi} would not have helped, as \ttt{event-stream} activated only on production (rather than testing or development).
Coarse-grained analysis at program boundaries, say via containment or system-call interposition~\cite{systrace:03}, would have not helped either as the programs importing \ttt{event-stream} already made use of system calls to access the disk and network.
Finally, static analysis would have been of little use, as \ttt{event-stream} encrypted its malicious payload.

Having the ability to toggle a library-level ``allow-deny'' security analysis on/off at runtime would have revealed the (unusual) resources touched by \ttt{event-stream}.
Analyzing the behavior \emph{within} the library itself is not critical:
  if any data exfiltration is happening, it will require calling out of the library and into the network---in \ttt{event-stream}'s case, using the \ttt{fs} library to modify a different library and then call \ttt{http} from the second library.
Both \ttt{fs} and \ttt{http} are part of the standard library, built into the runtime environment.
Other examples of interfaces that are available to the entire program include global variables, library importing, and the module cache---all of which are accessible by any third-party library.
% The key issue underlying the \ttt{event-stream} attack is that any third-party fragment of an application has unrestricted access to the functionality available to the rest of application.

@@

Switching-on a library-level profiling analysis 
  would quickly detect a slowdown and attribute it to the bottlenecked \ttt{minimatch}.
Wrapping library interfaces with profiling logic can be of aid to constructing a model of the current workload.
Such profiling could operate at a high resolution in time and space---at every function call entering a library and on hundreds of libraries across an application---but does not need to track detailed operations such as direct variable accesses.
Each library wrapper can collect profiling statistics at its own boundary, aggregating summaries into a global structure ordering libraries by resource consumption.

\heading{Type Invariant Discovery}
Extracting type information in at the library boundary is helpful in a variety of scenarios. %, as type safety is an important property helpful in variety of scenarios. 
Types can be used to
  (i) identify library invariants to be preserved during code modifications,
  (ii) generate (machine-checkable) library documentation, or 
  (iii) guide library synthesis and regeneration~\cite{daikon}.
This is especially important in dynamic programming languages:
  in the absence of static type signatures, there is not much one can say about a library without executing it and inspecting its properties.

As a case in point, consider the \ttt{gRPC} library for serializing and de-serializing objects~\cite{grpc}.
To use it, developers have to provide a protocol-buffer specification describing the types of values that will be serialized.
Given a library---\eg \ttt{bignum}, \ttt{crypto}---a developer has to first call it manually, take note of the result's type, and then fill in the protobuf spec.
This process has to be repeated with every change, often due to library updates or changes in the consuming program's structure.

Library-level dynamic analysis can be used to discover such type assertions or invariants.
The analysis would consult the (static) definition of a type system, capturing the type of values at the boundaries of libraries by observing their arguments during the execution of the program.
%% TODO: such as the simply-typed lambda calculus augmented with objects and union types.

@@

  \item \textbf{Fracture:}
\sys starts by recursively dismantling a program into its dependencies. % ---pieces of software implement a computation or functionality.
This is achieved by re-wiring the language's \ttt{import} function to go through \sys, resulting in \sys walking the program's recursive dependency structure at runtime.
During this phase, \sys has to determine the granularity of the analysis (\eg top-level libraries, a specific library \etc) in order to apply transformations at the correct level and map the provided analysis hooks to the corresponding libraries.

@@

  \item \textbf{Reassembly}
Finally, \sys reassembles individual modified libraries back into the program's original structure.
The most important challenge during this phase is the treatment of the library cache~\sx{bg1}.
The cache needs to be augmented to support multiple wrappers per library, each capturing a part of the overall analysis.
% without breaking the program's semantics.
% ensure every fragment finds its place during dependency reassembly,

@@

\subsection{Fracture}
\label{one}

When a \sys-augmented program starts, it first loads the analysis file provided by the developer. 
The file may specify a subset of libraries whose boundaries are of interest or a subset of libraries that should \emph{not} be analyzed.
Among other things, \sys needs to determine the library boundaries of interest and the granularity of analysis.
To do this, it extracts an approximation of the dependency graph by traversing library files.
Using this graph, it processes the analysis file to extract a mapping from library identifiers to analysis hooks.
It also checks for constructs not associated with libraries---for example, whether the analysis includes global variables, library-local constructs, standard libraries \etc
\sys then proceeds to dynamically replace the implementation of \ttt{import} and launch the program:
  rather than simply locating and loading a library, calls to \ttt{import} now yield to \sys.

@@

%FIXME: Needs examples, especially the context
For each analyzed library, \sys needs to place hooks all around its boundary---not just its interface (Fig.~\ref{fig:shadowing}).
This is achieved in three logical steps:
(i) transforming the library's context, a mapping from names to values that are available from outside library,
(ii) interpreting the library within this context, so that all names bind and resolve to \sys-augmented values, and
(iii) transforming the library's \ttt{export} value, \ie the library interface, once the interpretation is complete.
Before discussing \emph{where} each transformation is applied, however, we show \emph{how} they are applied.

@@

To achieve this, \sys first needs to prepare a transformed copy of the library's context---a map from variable names that are (expected to be) in scope to their values.
\sys creates an auxiliary hash table mapping names to transformed values.
Names correspond to any name that, by the language definition, is accessible by the library and resolves to a value outside that library, such as globals, built-ins, module-locals, \etc
Transformed values are created by applying \ttt{wrap} to values in the context, adding the provided analysis hooks.

@@

This section details the implementation of \sys for server-side JavaScript (Node.js v8.9.4) in about 1.5K LoC~\sx{impl1},
and the three analyses developed atop \sys~\sx{impl2}.
% We start with the internals of \sys's implementation, and then describe
The differences between JavaScript and other languages are left for \S\ref{reqs}. 
% How other environments diverge from JavaScript is discussed in a later section~\sx{reqs}.

@@

% The resolution algorithm is somewhat convoluted, because it depends on several different facts (including the type of the file requested, whether it is a globally installed, whether it is a directory \etc).
% It does not require any \sys support beyond copying the directory that contains the source code of the all the modules onto the remote host.
% \sys interposes on all of these steps to facilitate transformations.
\sys augments all of these steps.
Interposing on resolution (R) makes the module identifier available to \sys without affecting the (incredibly convoluted!) module resolution algorithm.
If the module's type corresponds to a module that can be analyzed by \sys, \sys fetches the corresponding analysis during loading (L).
Wrapping (W) and evaluation (E) are where \sys transforms the module boundary.
\sys replaces Node's wrapper function to pass an additional argument, the modified context \ttt{CTX}.
\sys comes with a hard-coded list of variable names available to the code of a module, such as \ttt{require} and \ttt{Array};
  the list contains about 150 entries and corresponds to the specific versions of EcmaScript and Node.
Identifying names coming from EcmaScript was relatively easy, as the standard makes them explicit.
Node's global names are described at various parts of the documentation, but library-local names required close inspection of Node's internals; fortunately, they were only five names.

@@

As the three analyses are too complex to include in the paper, we present here a trivial analysis---one that counts all accesses to global variables from a module \ttt{serial}:

@@

\heading{Security Analysis}
To address the security concerns of third-party libraries, we developed an on-off policy that analyzes accesses for every library-to-library combination.
The analysis treats built-in libraries and global variables as modules,
% and generates a list of permissions for each of their fields.
and develops a permission-like model where individual fields are governed by permission sets containing combinations of on and off permissions.
At the start of the analysis all permissions are set to off (\ie default-deny), and gradually turn on based on the accesses they detect.
Example accesses include:
 (i) reading a value, including assigning it to a variable and passing it around to other modules;
 (ii) modifying or deleting a value; and
 (iii)  executing a value---\eg a function or a method---or invoking a constructor (usually prefixed by \ttt{new}).

The resulting permission sets are organized as collections of maps, one per library, indexed by object-paths---\eg \ttt{require("Math").add: ON}.
% that correspond to values of other modules or global-like language names.

@@

  \item \textbf{Q3} How does it perform? We answer this question here.
  For the most libraries, \sys overheads are under 5\%~\sx{meso}.
  \sys is over an order-of-magnitude faster than Jalangi, a state-of-the-art dynamic analysis framework~\sx{meso}.
  By executing on unmodified runtimes, \sys has significantly better compatibility:
    to execute, Jalangi requires significant library modifications~\sx{meso}.
  \sys scales to three large applications with hundreds of libraries while interposing on several thousands of objects~\sx{macro}.
  Most of the overheads come from tracking global variables, but loading-time wrapping and runtime interposition overheads are negligible~\sx{micro}
  % The majority of the overheads come from the use of \ttt{with}, a

@@

\begin{figure*}[t]
  \centering
   \includegraphics[width=\textwidth]{./figs/micro-packages.pdf}
  \caption{
    \textbf{Runtime overhead.}
    The plot shows the runtime overhead of the three analyses for 50 libraries against normal (vanilla) execution~\cf{meso}.
  }
  \label{fig:micro-packages}
  \vspace{-3mm}
\end{figure*}

@@

In terms of analysis, both systems are configured to perform dynamic frequency analysis of accesses to global variables.
The analysis is a common denominator between \sys and Jalangi, designed and implemented from scratch to ensure a % fair and 
  meaningful comparison between the two frameworks.
Such analyses are useful for understanding program components interact with global state---\eg for generating remote-procedure stubs or scaling out functional components~\cite{ignis}.

Fig.~\ref{fig:meso} presents the comparison between \sys and Jalangi.
The core of the analysis requires a few lines, but expressing it in \sys requires 4$\times$ fewer lines of code.
% the effort of employing \sys as a library was also significantly lower than that of Jalangi2, for which we relied on a Docker container to simplify the framework's setup.
The performance results show that \sys performs better than Jalangi, at times by a significant margin (\ie more than 10$\times$ for 13 benchmarks).

Implemented as a custom interpreter, Jalangi exists at a different point in the trade-off space than \sys.
On the one hand, it is significantly more fine-grained than \sys, capable of expressing and executing analyses at the granularity of individual expressions.
On the other hand, it results in significantly higher incompatibility and runtime overhead---even when the analysis does not make use of its features.

@@

\begin{table}[b]
\center
\footnotesize
\setlength\tabcolsep{3pt}
\caption{
  \footnotesize{
    \textbf{Applying \sys to three large applications}.
    The table shows the characteristics and runtime overheads of applying the three analyses to three large applications~\cf{macro}.
  }
}
\begin{tabular*}{\columnwidth}{l @{\extracolsep{\fill}} ccc}
\toprule
                                     & KoaBlog~\cite{koa}    & Moeda~\cite{moeda}   &  Term/zr~\cite{terminalizer} \\
\midrule
Structure                            &                   &                      &              \\
~~Size (MB)                          & 41                &  29                  &   262        \\
~~Code Size (KLoC)                   & 127               &  79                  &   39         \\
~~Top-level Modules, statically      &  24               &  7                   &    33         \\
~~Total Modules, statically (npm)    &  432              &  260                 &    1084       \\
~~Total Modules, dynamically (\sys)  &  1507             &   729                &     2355      \\
%                                     &                   &                      &              \\
Performance (s)                      &                   &                      &              \\
~~Baseline                           &  0.97             &  1.27                &    0.754      \\
~~Security Analysis                  &  1.48             &  2.00                &    3.346      \\
~~Performance Diagnosis              &  1.30             &  2.684               &    2.684      \\
~~Type Invariant Discovery           &  1.32             &  2.036               &    2.615      \\     
\bottomrule
\end{tabular*}
\label{tab:macro}
\vspace{-5mm}
\end{table}

@@

The differences between the number of sub-modules detected statically (by \ttt{npm ls}) and the ones observed by \sys are due to a few reasons.
One is that \sys does not report accesses if a library is not accessed at runtime, whereas \ttt{npm} traverses and reports on the entire dependency structure.
\sys analyzes modules that are part of the standard library (some of which have themselves internal dependencies),  not shown by \ttt{npm}.
Finally, \sys generates several different return wrapped objects for the same libraries~\sx{three}.

Applying \sys to these applications generates analysis results that are 9--132$\times$ larger than the ones for single libraries.
However, the performance of analyzed code is on average still within 2--3$\times$ over the baseline performance.
The size of the resulting JSON files raises the challenge of analysis interpretability---just by running Terminalizer with \ttt{--help} returns more than 6K fragments from several (hundreds of) libraries.
Custom \ttt{onExit} analysis routines post-process \sys's results to compress by module name---\ie squashing duplicate reports by human-readable name, not file-system module identifier.
This can affect the results of multiple imports with the same name at different parts of the tree that would indeed correspond to different libraries.
% For example, importing two different versions of a library at two different parts of the dependency tree will result in to two different with the same name.
We also squash cache entries that correspond to one module imported by multiple modules, which would create separate entries in \sys's augmented cache, but results in a single count for Tab.~\ref{macro} (for \sys's treatment of the module cache, see~\S\ref{three}).
Confirming that \sys performs correctly under these scenarios is one part of the motivation behind the synthetic micro-benchmarks shown earlier~\sx{micro}.
